\section{Activities}

\subsection{PHASE Repository}
\label{sec:repo}
PHASE will curate a repository of amplitude models. The models will consist of computer codes with executable examples and documentation. Care will be taken to ensure proper attribution of the contributed code and extensive documentation of the properties, the applicability and the limitations of the available models. The repository web interface will provide the infrastructure for discussion, review and development of the model code. An example for such an interface is \href{https://about.gitlab.com/}{gitlab}. 

The PHASE repository aims at providing an active and lively forum for exchange between analysts, software developers and theorists. To facilitate this, the repository will be completely open for contributions. All contributed code will be distributed under the Creative Commons
\href{https://creativecommons.org/licenses/by-sa/4.0/}{Attribution-ShareAlike 4.0 International} license. The members of the panel will assume the roles of moderators on the discussion and review portion of the repository website. All participants agree to adhere to the \href{https://rfc.zeromq.org/spec:42/C4/}{ZeroMQ collective code construction contract C4}, which will be updated and adapted to the need of the community by the PHASE panel.

PHASE will provide the means to attribute the models submitted to the repository to the original authors. Original publications will be used if they are available. In cases where a model is created collaboratively on the repository, alternative methods of attribution, such as \href{http://openbadges.org}{software badges} will be provided. When a collaborative model reaches a state of sophistication that allows it to be used in an analysis, PHASE will assist in the creation of a collaborative publication with an authorlist containing all contributers.

\subsection{Hadron Amplitude Hackathons}
\label{sec:hackathon}
PHASE will organize regular workshops, which will take the form of Hackathons where experts work on a concrete problem, such as providing a certain parameterization to the analysts. Each hackathon will have a concrete goal and will deliver actual software, which is provided to the experiments through the PHASE repository. The attribution of the developed models follows the guidelines lined out in subsection \ref{sec:repo}.

In order to test and develop these tools the experimental collaborations will be asked to provide simulated data, or where applicable, measured data sets. 


\subsection{Annual review on amplitude analysis}
\label{rec:review}
The members of the panel compile and annual review article to be published in a major journal. The aim of this article is to review the state of the art of hadronic amplitude models and define best practices. The panel ensures that the models and techniques discussed in the PHASE review are made available in the PHASE repository and encourages an open discussion in the repository forum.

\subsection{Amplitude model validation}
\label{sec:validation}
PHASE will provide the expertise to validate the models used by individual analyses by the partaking experiments. This validation is a community service, which can be tapped into by the collaborations as a resource to inform the internal review of ongoing analyses. Validation can take two forms: the experiments can directly use the source code provided and reviewed in the PHASE repository for their analyses. Or they can proof, using toy Monte Carlo samples, that the models used in a particular analysis give identical results (or possibly deviate) from the PHASE reference implementations.

\subsection{Community building}
\label{sec:community}
An important goal of PHASE is to intensify the exchange of ideas between the participants. In addition to hosting the model repository and organising the amplitude hackathons, PHASE will facilitate community building measures. Experiment and theory liaisons will identify common ground and potential synergies accross experiments and theory groups. They will establish contacts between students working on related projects and engage in knowledge transfer.

Distributed teamwork is a considerable challenge and needs modern communication tools to have a chance of blossoming. PHASE will operate a virtual team workplace, such as a \href{http://slack.com}{slack} community to provide an address for life questions and exchange on all issues surrounding amplitude analysis and hadron physics.    

\subsection{Open data advocacy}
\label{sec:opendata}
PHASE recognizes the authority of all experimental collaborations over their data. In order to further the usage of data accross the community the network will support collabortions when they decide to publish a dataset, usually after the initial analysis of the data has been published by the primary authors of the data. 

The support is technical and organisational in nature and aims to develop standardised data exchange formats.  


\subsection{PHASE fellowships}
\label{sec:fellowships}
PHASE will seek to provide four 2-year fellowships every two years. Two will have theoretical and two of theses positions will have experimental/computational focus. The fellowships will be awarded to young researchers with expertise in amplitude analysis. They will join the core team, taking up responsibilities for the technical tasks and will work on concrete projects inside the PHASE network. 

PHASE will strive to colocate its fellows. Travel funds will be provided taking into account the particular role of network multipliers the fellows will play.

All PHASE fellows will become members of the PHASE annual review authorlist for the duration of their fellowship plus the following year.     
